\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-14 sections/methods.tex
Fix: Figure 7 issues

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or the \ac{esv}s.
  In order to assign taxonomies to a particular sequence a taxonomy database and a query tool are necessary.
  The taxonomy database contains the collection of 16S sequences of microorganisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006}, SILVA 138~\cite{Quast2012} and the \ac{ncbi} (16S RefSeq as of Oct 2021)~\cite{Sayers2009} databases for taxonomy assignment.
  SILVA and \ac{gg} are two popular 16S databases used for taxonomy identification and the \ac{ncbi} RefSeq nucleotide database contains 16S rRNA sequences as a part of two BioProjects - 33175 and 33317.
  The three databases vastly differ in terms of their last update status - \ac{gg} was last updated on May 2013, SILVA was last updated on August 2020 at the time of writing and \ac{ncbi} is updated regularly as new sequences are curated.
  These databases were downloaded and built using the RESCRIPt \ac{qiime2} plugin~\cite{iiRESCRIPtReproducibleSequence2021}.
  The Naive Bayes classifier and the \ac{ncbi} blast used as the query tools in this study were from the \ac{qiime2} package and the parameters used were the defaults of the package.
  During the assignment, a representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a given Genus; the second, more likely reason, is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.
  The assignment between SILVA and the other two databases were originally significantly different ($40\%$ mismatch) even at the Phylum level.
  However, this was fixed by making minor adjustments to the taxonomic names, such as changing Bacteroidota to Bacteroidetes in the SILVA Phylum assignments.
  The full list of changes can be found in \texttt{figure4ab\_data.py} in the data and scripts  repository.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:micone_tools}.

>>>>

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or the \ac{esv}s.
  In order to assign taxonomies to a particular sequence a taxonomy database and a query tool are necessary.
  The taxonomy database contains the collection of 16S sequences of microorganisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006} (99\% identity), SILVA 138~\cite{Quast2012} (99\% identity) and the \ac{ncbi} (16S RefSeq as of Oct 2021)~\cite{Sayers2009} databases for taxonomy assignment.
  SILVA and \ac{gg} are two popular 16S databases used for taxonomy identification and the \ac{ncbi} RefSeq nucleotide database contains 16S rRNA sequences as a part of two BioProjects - 33175 and 33317.
  The three databases vastly differ in terms of their last update status - \ac{gg} was last updated on May 2013, SILVA was last updated on August 2020 at the time of writing and \ac{ncbi} is updated regularly as new sequences are curated.
  These databases were downloaded and built using the RESCRIPt \ac{qiime2} plugin~\cite{iiRESCRIPtReproducibleSequence2021}.
  The Naive Bayes classifier and the \ac{ncbi} blast used as the query tools in this study were from the \ac{qiime2} package and the parameters used were the defaults of the package.
  During the assignment, a representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a given Genus; the second, more likely reason, is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.
  The assignment between SILVA and the other two databases were originally significantly different ($40\%$ mismatch) even at the Phylum level.
  However, this was fixed by making minor adjustments to the taxonomic names, such as changing Bacteroidota to Bacteroidetes in the SILVA Phylum assignments.
  The full list of changes can be found in \texttt{figure4ab\_data.py} in the data and scripts  repository.
  The list of tools used in this step, along with their modules and references are provided in Table~\ref{tab:micone_tools}.
